---
title: "FantasyFootballPredictor"
output:
  pdf_document: default
  html_document: default
---

\newcommand{\E}{\mathbb{E}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\Corr}{\mathrm{Corr}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\fix}[1]{\textcolor{red}{\textbf{\large (#1)\normalsize}}}

```{r setup, include=FALSE}
suppressPackageStartupMessages(library(knitr)) #makes pdfs
suppressPackageStartupMessages(library(latex2exp))
suppressPackageStartupMessages(library(tidyverse)) #good library for data manipulation, includes dplyr and ggplot
# you can read more about the tidyverse at: https://r4ds.had.co.nz/
suppressPackageStartupMessages(library(Lahman)) #good library for baseball
suppressPackageStartupMessages(library(car)) #to check variance inflation
suppressPackageStartupMessages(library(nflfastR)) 
suppressPackageStartupMessages(library(janitor)) 
suppressPackageStartupMessages(library(glue)) 
suppressPackageStartupMessages(library(stringr)) 
suppressPackageStartupMessages(library(rvest)) 
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(party))
suppressPackageStartupMessages(library(randomForest))
suppressPackageStartupMessages(library(sjmisc))
install.packages("plyr")
knitr::opts_chunk$set(echo = TRUE)
```



## R Markdown
PLAYER DATASET
```{r}
df <- load_player_stats(c(2018,2019,2021))
df <- filter(df, completions < 2, carries > 5)
team_abb <- read.csv('nfl_teams.csv')
team_abb <- select(team_abb, Name, Abbreviation)
names(team_abb) <- c('team', 'recent_team')
rushingStats <- merge(df, team_abb, by = 'recent_team')
rushingStats <- select(rushingStats, 1:6, 22:28, 42, 49)
rushingStats$team <- word(rushingStats$team, -1)
playerData <- select(rushingStats, player_name, team, season, week, 
                     carries, rushing_yards, rushing_tds, fantasy_points)
head(playerData)
```




FUNCTIONS TO FIND PLAYERS TOTAL STAT UP TO THAT WEEK
YARDS
```{r}
func_total_yards <- function(weeks, playerName, team_) {
  upToWeek <- filter(rushingStats, week < weeks, player_name == playerName, 
                     team == team_)
  return(mean(upToWeek$rushing_yards))
}
```

CARRIES
```{r}
func_total_carries <- function(weeks, playerName, team_) {
  upToWeek <- filter(rushingStats, week < weeks, player_name == playerName, 
                     team == team_)
  return(mean(upToWeek$carries))
}
```

TDS
```{r}
func_total_tds <- function(weeks, playerName, team_) {
  upToWeek <- filter(rushingStats, week < weeks, player_name == playerName,
                     team == team_)
  return(mean(upToWeek$rushing_tds))
}
```



FUNCTIONS TO CALCULATE PLAYERS AVERAGE STAT PAST 5 WEEKS
L5 AVG YARDS
```{r}
func_five_yards <- function(weeks, playerName, team_) {
  upToWeek <- filter(rushingStats, week < weeks, week > weeks-6,
                     player_name == playerName, team == team_)
  return(mean(upToWeek$rushing_yards))
}
```

L5 AVG CARRIES
```{r}
func_five_carries <- function(weeks, playerName, team_) {
  upToWeek <- filter(rushingStats, week < weeks, week > weeks-6,
                     player_name == playerName, team == team_)
  return(mean(upToWeek$carries))
}
```

L5 AVG TDS
```{r}
func_five_tds <- function(weeks, playerName, team_) {
  upToWeek <- filter(rushingStats, week < weeks, week > weeks-6,
                     player_name == playerName, team == team_)
  return(mean(upToWeek$rushing_tds))
}
```


Adding in last 5 game data
```{r}
attach(playerData)
playerData <- mutate(playerData, 
                  avgYardsSF = mapply(func_total_yards, week, player_name, team),
                  avgCarriesSF = mapply(func_total_carries, week, player_name, team),
                  avgTDSF = mapply(func_total_tds, week, player_name, team),
                  L5AVGYards = mapply(func_five_yards, week, player_name, team),
                  L5AVGCarries = mapply(func_five_carries, week, player_name, team),
                  L5AVGTDS = mapply(func_five_tds, week, player_name, team))
head(playerData)
```



```{r}
attach(playerData)
playerData <- mutate(playerData, avgYPC = avgYardsSF / avgCarriesSF)
playerData <- mutate(playerData, L5YPC = L5AVGYards / L5AVGCarries)
playerData$YPC <- rushing_yards/carries
head(playerData)
```





<!-- ```{r} -->
<!-- draft_picks <- read_csv("https://raw.githubusercontent.com/leesharpe/nfldata/master/data/draft_picks.csv") -->
<!-- draft_picks <- filter(draft_picks, season > 1995, position == 'RB') -->
<!-- draft_picks$pickNumber <- (draft_picks$round-1)*32 + draft_picks$pick -->
<!-- draft_picks <- select(draft_picks, pfr_name, pickNumber) -->
<!-- ``` -->



<!-- ```{r} -->
<!-- attach(draft_picks) -->
<!-- draft_picks <- mutate(draft_picks,  -->
<!--                       player_name = paste(str_sub(pfr_name, 1,1),  -->
<!--                                           word(pfr_name,-1), sep = ".")) -->
<!-- draft_picks <- select(draft_picks, player_name, pickNumber) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- playerData <- left_join(playerData, draft_picks) -->
<!-- head(playerData) -->
<!-- ``` -->



GAME DATASET 
https://jakesdatalab.com/post/gathering-historical-nfl-weather-data/
```{r} 
weeks <- c(1:17)
years <- c(2018,2019,2021)
weather_weeks_and_years <- crossing(year = years, week = weeks) # generate all unique combinations

# function to generate urls
generate_urls <- function(year, week) {
  full_url <- glue::glue("http://nflweather.com/en/week/{year}/week-{week}/")
}

# pass weeks and years through function
url_list <- pmap(weather_weeks_and_years, generate_urls)
head(url_list)
```



```{r}
scrape_weather_data <- function(webpage_url) {
  webpage_url %>% 
    read_html() %>% 
    html_table() %>%
    .[[1]] %>% 
    clean_names() %>%
    select(away, home, forecast, wind) %>%
    mutate(season = str_sub(webpage_url, start= 31, end = 34),
           week = str_sub(gsub('.*\\-', '', webpage_url), start = -3, end = -2),
           wind = as.numeric(gsub( "m.*$", "",wind)),
           temperature = ifelse(forecast == 'DOME', 71, gsub( "f.*$", "", forecast)),
           weather = gsub(".*? ", "", forecast)) %>%
    pivot_longer(cols = c('away', 'home'), values_to = 'team') %>% 
    select(-name, -forecast) %>% 
    select(team, season, week, temperature, wind, weather)
}
```

```{r}
weather_data <- map_df(url_list, scrape_weather_data)
weather_data
```


GAME DATA
```{r}
game_data <- read.csv('spreadspoke_scores.csv')
game_data <- filter(game_data, schedule_season > 2008)
game_data <- mutate(game_data, home = word(game_data$team_home,-1), 
                    away = word(game_data$team_away, -1))
game_data <- game_data %>% 
  pivot_longer(cols = c('team_away', 'team_home'), values_to = 'team') %>%
  select(team, schedule_season, schedule_week, team_favorite_id, spread_favorite,
         over_under_line, weather_temperature, home, away)
game_data <- rename(game_data, recent_team = team_favorite_id)
team_abb <- read.csv('nfl_teams.csv')
team_abb <- select(team_abb, Name, Abbreviation)
names(team_abb) <- c('Favorite', 'recent_team')
game_data <- merge(game_data, team_abb, by = 'recent_team')
game_data$spread_favorite <- ifelse(game_data$team == game_data$Favorite, 
                    game_data$spread_favorite, game_data$spread_favorite * -1)
game_data <- rename(game_data, season = schedule_season, week = schedule_week,
                    spread = spread_favorite)
game_data$team <- word(game_data$team,-1)
game_data <- merge(game_data, weather_data, by = c('season', 'week', 'team'))
game_data <- select(game_data, -c('recent_team', 'weather_temperature'))
game_data$proj_team_points <- game_data$over_under_line / 2 + ((-1/2) *
                                            game_data$spread)
game_data$opponent <- ifelse(game_data$team == game_data$home, game_data$away,
                             game_data$home)
game_data <- select(game_data, -c(home, away))
game_data$week <- as.numeric(game_data$week)
head(game_data)
```





TEAM DATASET
```{r}
data <- load_pbp(c(2018,2019,2021))
attach(data)
data$season = substr(game_id,0,4)
data$week <- substr(game_id,5,7)
data$count <- 1
data$season <- substr(data$game_id,0,4)
rushPlays <- filter(data, play_type == "run", qb_scramble == 0)
head(rushPlays)
```

```{r}
func_avg_run_rate <- function(weeks, dteam) {
  upToWeek <- filter(dRunRate, week < weeks, team == dteam)
  return(mean(upToWeek$dRunRate))
}
```

```{r}
func_five_run_rate <- function(weeks, dteam) {
  upToWeek <- filter(dRunRate, week < weeks, week > weeks-6, team == dteam)
  return(mean(upToWeek$dRunRate))
}
```




```{r}
offensive_plays <- filter(data, play_type == 'run' | play_type == 'pass')
offensive_plays$play_type <- ifelse(offensive_plays$qb_scramble == 1, 
                                    'pass', offensive_plays$play_type)
head(offensive_plays)
```

```{r}
defense <- offensive_plays %>% group_by(defteam, season, week)
defense$week <- as.numeric(str_sub(defense$week,2))
dRunRate <- as.data.frame(summarise(defense, sum(play_type == 'run') / (
  sum(play_type == 'run') + sum(play_type == 'pass'))))
names(dRunRate) = c('team', 'season', 'week', 'dRunRate')
head(dRunRate)
```


```{r}
dfunc_avg_run_rate <- function(weeks, dteam) {
  upToWeek <- filter(dRunRate, week < weeks, team == dteam)
  return(mean(upToWeek$dRunRate))
}
```


```{r}
dfunc_five_run_rate <- function(weeks, dteam) {
  upToWeek <- filter(dRunRate, week < weeks, week > weeks-6,
                     team == dteam)
  return(mean(upToWeek$dRunRate))
}
```

```{r}
attach(dRunRate)
dRunRate <- mutate(dRunRate, 
                   dRunRate = mapply(dfunc_avg_run_rate, week, team),
                   dL5_runRate = mapply(dfunc_five_run_rate, week, team))
dRunRate
```


```{r}
offense <- offensive_plays %>% group_by(posteam, week)
offense$week <- as.numeric(str_sub(offense$week,2))
oRunRate <- as.data.frame(summarise(offense, sum(play_type == 'run') / (
  sum(play_type == 'run') + sum(play_type == 'pass'))))
names(oRunRate) = c('team', 'week', 'o_run_rate')
```

```{r}
ofunc_avg_run_rate <- function(weeks, dteam) {
  upToWeek <- filter(oRunRate, week < weeks, team == dteam)
  return(mean(upToWeek$o_run_rate))
}
```


```{r}
ofunc_five_run_rate <- function(weeks, dteam) {
  upToWeek <- filter(oRunRate, week < weeks, week > weeks-6, team == dteam)
  return(mean(upToWeek$o_run_rate))
}
```


```{r}
attach(oRunRate)
RunRate <- mutate(dRunRate, 
                   Oavg_runRateSF = mapply(ofunc_avg_run_rate, week, team),
                   OL5_runRate = mapply(ofunc_five_run_rate, week, team))

head(RunRate)
```


Defensive Stats
```{r}
opp_def <- rushPlays %>% group_by(season, defteam, week)
opp_def$week <- as.numeric(str_sub(opp_def$week, 2))
defSeasonYards <- summarize(opp_def, sum(yards_gained))
defYPG <- as.data.frame(defSeasonYards)
defCPG <- as.data.frame(summarise(opp_def, sum(count)))
names(defYPG) <- c('season', 'team', 'week', 'yards_allowed')
names(defCPG) <- c('season', 'team', 'week', 'carries_allowed')
defStats <- merge(defYPG, defCPG, by = c('season', 'team', 'week'))
head(defStats)
```

Function to calculate team total rushing yards up to that week
```{r}
attach(defStats)
func_avg_dyards <- function(weeks, dteam) {
  upToWeek <- filter(defStats, week < weeks, team == dteam)
  return(mean(upToWeek$yards_allowed))
}
```

Function to calculate teams carries allowed up to that week
```{r}
func_avg_dcarries <- function(weeks, dteam) {
  upToWeek <- filter(defStats, week < weeks, team == dteam)
  return(mean(upToWeek$carries_allowed))
}
```

Function to calculate teams total yards allowed past 5 weeks
```{r}
func_five_dyards <- function(weeks, dteam) {
  upToWeek <- filter(defStats, week < weeks, week > weeks-6,
                     team == dteam)
  return(mean(upToWeek$yards_allowed))
}
```

Function to calculate teams total carries allowed past 5 weeks
```{r}
func_five_dcarries <- function(weeks, dteam) {
  upToWeek <- filter(defStats, week < weeks, week > weeks-6,
                     team == dteam)
  return(mean(upToWeek$carries_allowed))
}
```



```{r}
attach(defStats)
defStats <- mutate(defStats, 
                  avgYardsAllowed = mapply(func_avg_dyards, week, team),
                  avgCarriesAllowed= mapply(func_avg_dcarries, week, team),
                  avgL5YardsAllowed = mapply(func_five_dyards, week, team),
                  avgL5CarriesAllowed = mapply(func_five_dcarries, week, team))
head(defStats)
```



```{r}
team_Stats <- merge(defStats, RunRate, by = c('season', 'team', 'week'))
head(team_Stats)
team_Stats <- select(team_Stats, 1:3, 6:13)
team_Stats <- team_Stats[order(team, week),]
merging <- team_abb
names(merging) <- c('teamFull', 'team')
team_Stats <- merge(merging, team_Stats, by = 'team')
team_Stats <- select(team_Stats, -team)
team_Stats <- rename(team_Stats, opponent = teamFull)
team_Stats$opponent <- word(team_Stats$opponent,-1)
team_Stats <- mutate(team_Stats, 
                     avg_ypc_allowed = avgYardsAllowed/avgCarriesAllowed,
                     L5_ypc_allowed = avgL5YardsAllowed / avgL5CarriesAllowed)
head(team_Stats)
```


```{r}
func_findPlayer <- function(description){
  vec <- unlist(str_split(description, " "))
  for(i in 1:length(vec)){
    if(vec[i] == "left" || vec[i] == "up" || vec[i] == "right") {
      break
    }
  }
  return(vec[i-1])
}
```

```{r}
goalLine <- filter(rushPlays, goal_to_go == 1, ydstogo < 5)
goalLine <- mutate(goalLine, player = mapply(func_findPlayer, goalLine$desc),
                   season = str_sub(game_id,1,4))
goalLine <- filter(goalLine, str_sub(player,2,2) == '0' | str_sub(player,2,2) == "1" | 
                   str_sub(player,2,2) == "2" |  str_sub(player,2,2) == "3" |
                   str_sub(player,2,2) == "4" | str_sub(player,2,2) == "5" | 
                   str_sub(player,2,2) == "6" | str_sub(player,2,2) == "7" | 
                   str_sub(player,2,2) == "8" | str_sub(player,2,2) == "9")
goalLine$player_name = str_sub(goalLine$player,4,-1)
goalLine$ydLine = word(goalLine$yrdln,-1)
goalLine <- select(goalLine, posteam, week, season, player_name, ydLine)
goalLine$goalLineCarry = 1
goalLine$week <- as.numeric(str_sub(goalLine$week,2,-1))
goalLine <- rename(goalLine, team = posteam)
goalLine

```


```{r}
names(merging) <- c('teamFull', 'team')
goalLine <- merge(merging, goalLine, by = 'team')
goalLine <- select(goalLine, -team)
goalLine <- rename(goalLine, team = teamFull)
goalLine$team <- word(goalLine$team,-1)
goalLine <- unique(goalLine)
goalLine <- group_by(goalLine, player_name, season, week, team)
goalLine <- as.data.frame(summarise(goalLine, sum(goalLineCarry)))
names(goalLine) <- c("player_name", "season", "week", "team", "goalLineCarry")
goalLine$season <- as.numeric(goalLine$season)
head(goalLine)
```


```{r}
playerData <- left_join(playerData, goalLine, by = c("player_name", "team", "season", "week"))
playerData$goalLineCarry <- ifelse(is.na(playerData$goalLineCarry), 0, playerData$goalLineCarry)
head(playerData)
```


```{r}
func_avg_glCarries <- function(weeks, playerName, teams, seasons) {
  upToWeek <- filter(playerData, week < weeks, team == teams, 
                     player_name == playerName, season == seasons)
  return(mean(upToWeek$goalLineCarry))
}
```

```{r}
func_five_glCarries <- function(weeks, playerName, teams, seasons) {
  upToWeek <- filter(playerData, week < weeks, week > weeks-6,
                     team == teams, player_name == playerName, season == seasons)
  return(mean(upToWeek$goalLineCarry))
}
```


```{r}
playerData <- mutate(playerData, 
          avgGLC = mapply(func_avg_glCarries, week, player_name, team, season),
          L5GLC = mapply(func_five_glCarries, week, player_name, team, season))
head(playerData)
```



EXPECTED CARRIES DATASET
```{r}
expected_carries <- select(playerData, player_name, team, season, week, 
                           avgCarriesSF, L5AVGCarries, carries, fantasy_points)
game_team <- merge(game_data, select(team_Stats, opponent, week, 
            avgCarriesAllowed, avgL5CarriesAllowed, dRunRate, dL5_runRate), 
            by = c('week', 'opponent'))
expected_carries <- merge(expected_carries, game_team, by = c('season','week','team'))
expected_carries <- expected_carries[order(expected_carries$player_name),]
expected_carries <- expected_carries %>% relocate(player_name)
expected_carries <- filter(expected_carries, week >= 6)
expected_carries <- unique(expected_carries)
expected_carries  <- na.omit(expected_carries)
expected_carries
```

```{r}
carries_train_data <- filter(expected_carries, season == 2018 | season == 2019)
carries_test_data <- filter(expected_carries, season == 2021)
head(carries_train_data)
head(carries_test_data)
```

```{r}
rf_carries_model <- randomForest(carries ~ avgCarriesSF + L5AVGCarries + spread + temperature +
                                 wind + weather + avgCarriesAllowed + avgL5CarriesAllowed + dRunRate +
                                 dL5_runRate, data = carries_train_data, mtry = 2)
rf_carries_model <- tuneRF(select(carries_train_data, avgCarriesSF, L5AVGCarries, spread, temperature,
                                 wind, weather, avgCarriesAllowed, avgL5CarriesAllowed, dRunRate,
                                 dL5_runRate), carries_train_data$carries,  doBest = TRUE)
rf_carries_model
carries_train_data$expectedCarries <- predict(rf_carries_model, carries_train_data)
carries_test_data$expectedCarries <- predict(rf_carries_model, carries_test_data)
carries_test_data$c = carries_test_data$carries
carries_test_data
```
```{r}
team_Stats
```


EXPECTED RUSH YDS PER CARRY DATASET
```{r}
expected_YPC <- select(playerData, player_name, team, season, week, 
                           avgYPC, L5YPC, YPC)
game_team_YPC <- merge(game_data, select(team_Stats, opponent, week, 
            avg_ypc_allowed, L5_ypc_allowed), by = c('week', 'opponent'))
game_team_YPC
expected_YPC <- merge(expected_YPC, game_team_YPC, by = c('season', 'week','team')) 
game_team_YPC
expected_YPC <- unique(expected_YPC) 
expected_YPC <- filter(expected_YPC, week >= 6)
expected_YPC <- expected_YPC[order(expected_carries$player_name),]
expected_YPC <- expected_YPC %>% relocate(player_name)
expected_YPC <- na.omit(expected_YPC)
expected_YPC
```

```{r}
ypc_train_data <- filter(expected_YPC, season == 2018 | season == 2019)
ypc_test_data <- filter(expected_YPC, season == 2021)
ypc_train_data
ypc_test_data
```

```{r}
rf_ypc_model <- tuneRF(select(ypc_train_data, avgYPC, L5YPC, spread, proj_team_points,
                                 wind, weather, avg_ypc_allowed,  
                               L5_ypc_allowed), ypc_train_data$YPC, doBest = TRUE)
rf_ypc_model <- randomForest(YPC ~ avgYPC + L5YPC + spread + proj_team_points +
                                 wind + weather + avg_ypc_allowed + 
                               L5_ypc_allowed, data = ypc_train_data, mtry =1)
rf_ypc_model
ypc_train_data$expectedYPC <- predict(rf_ypc_model, ypc_train_data)
ypc_test_data$expectedYPC <- predict(rf_ypc_model, ypc_test_data)
ypc_test_data$ypc = ypc_test_data$YPC
ypc_test_data
```


```{r}
expected_TDS <- select(playerData, player_name, team, season, week, 
                        avgTDSF, L5AVGTDS, avgGLC, L5GLC,
                       rushing_tds)
expected_TDS <- merge(expected_TDS, game_team_YPC, by = c('season', 'week','team')) 
expected_TDS <- unique(expected_TDS) 
expected_TDS <- filter(expected_TDS, week >= 6)
expected_TDS <- expected_TDS[order(expected_carries$player_name),]
expected_TDS <- expected_TDS %>% relocate(player_name)
expected_TDS <- na.omit(expected_TDS)
expected_TDS
```

```{r}
td_train_data <- filter(expected_TDS, season == 2018 | season == 2019)
td_test_data <- filter(expected_TDS, season == 2021)
td_train_data
td_test_data
```


```{r}
rf_td_model <- tuneRF(select(td_train_data, avgTDSF, L5AVGTDS, avgGLC, proj_team_points,
                                 wind, weather, avg_ypc_allowed, 
                               L5_ypc_allowed), td_train_data$rushing_tds, doBest = TRUE)
rf_td_model <- randomForest(rushing_tds ~ avgTDSF + L5AVGTDS + avgGLC + proj_team_points +
                                 wind + weather + avg_ypc_allowed + 
                               L5_ypc_allowed, data = td_train_data, mtry = 2)
rf_td_model
td_test_data$expectedTDS <- predict(rf_td_model, td_test_data)
td_test_data$tds = td_test_data$rushing_tds
td_test_data
```

```{r}
func_avg_fantasy_points <- function(weeks, playerName, dteam, season) {
  upToWeek <- filter(playerData, week < weeks, team == dteam)
  return(mean(upToWeek$fantasy_points))
}
```

```{r}
func_avg_fantasy_points(4, "D.Johnson", "Cardinals", 2018)
```

```{r}
expected_carries$expectedCarries <- predict(rf_carries_model, expected_carries)
expected_TDS$expectedTDS <- predict(rf_td_model, expected_TDS)
expected_YPC$expectedYPC <- predict(rf_ypc_model, expected_YPC)
```


```{r}
func_L5_fantasy_points <- function(weeks, playerName, dteam, seasons) {
  upToWeek <- filter(playerData, week < weeks, week > weeks-6, 
                     player_name == playerName, team == dteam, season == seasons)
  return(mean(upToWeek$fantasy_points))
}
```


```{r}
expectedStats <- left_join(expected_carries, expected_TDS, 
                           by = c("player_name", "team", "season", "week"))
expectedStats <- left_join(expectedStats, expected_YPC, by = c("player_name", "team", "season", "week"))
expectedStats <- select(expectedStats, player_name, team, season, week, expectedCarries, expectedYPC, expectedTDS)
```




```{r}
attach(expectedStats)
expectedStats$expectedFantasyPoints <- expectedCarries*expectedYPC/10 + 6*expectedTDS
expectedStats <- filter(expectedStats, !is.na(expectedFantasyPoints))
head(expectedStats)
```


```{r}
fantasy_model <- select(expected_carries, player_name, team, season, week, fantasy_points)
fantasy_model <- left_join(fantasy_model, expectedStats, by = c("player_name", "team", "season", "week"))
fantasy_model <- mutate(fantasy_model, 
                  avgFantasyPoints = mapply(func_avg_fantasy_points, week, 
                                            player_name, team, season),
                  L5FantasyPoints = mapply(func_L5_fantasy_points, week, 
                                           player_name, team, season))
fantasy_model <- select(fantasy_model, player_name, team, season, week, fantasy_points,
                        expectedFantasyPoints, avgFantasyPoints, L5FantasyPoints)
fantasy_model <- filter(fantasy_model, !is.na(expectedFantasyPoints))
fantasy_model_train <- filter(fantasy_model, season== 2018 | season == 2019)
fantasy_model_test <- filter(fantasy_model, season == 2021)
```

```{r}
rf_fantasy_model <- randomForest(fantasy_points ~ expectedFantasyPoints +
                        avgFantasyPoints + L5FantasyPoints, data = fantasy_model_train)
fantasy_model_test$predictedFantasyPoints <- predict(rf_fantasy_model, fantasy_model_test)
fantasy_model$predictedFantasyPoints <- predict(rf_fantasy_model, fantasy_model)
```

```{r}
mean((fantasy_model_test$predictedFantasyPoints - fantasy_model_test$fantasy_points)^2)
mean((fantasy_model_test$expectedFantasyPoints - fantasy_model_test$fantasy_points)^2)
mean((fantasy_model_train$expectedFantasyPoints - fantasy_model_train$fantasy_points)^2)
```

```{r}
mean((filter(expected_carries, season == 2021)$expectedCarries -
   filter(expected_carries, season == 2021)$carries)^2)
mean((filter(expected_YPC, season == 2021)$expectedYPC -
   filter(expected_YPC, season == 2021)$YPC)^2)
mean((filter(expected_TDS, season == 2021)$expectedTDS -
   filter(expected_TDS, season == 2021)$rushing_tds)^2)
```


PREDICTS WHIICH PLAYER
```{r}
func_predict_player <- function(player1, player1team, player2, player2team, weeks, seasons){
  playerO <- filter(fantasy_model, player_name == player1, team == player1team, 
                    week == weeks, season == seasons)
  playerT <- filter(fantasy_model, player_name == player2, team == player2team,
                    week == weeks, season == seasons)
  if(sum(playerO$predictedFantasyPoints) > sum(playerT$predictedFantasyPoints)) {
    return(player1)
  }
  else{
    return(player2)
  }
}
```


```{r}
func_predict_player("J.Taylor", "Colts", "B.Scott", "Eagles", 13, 2021)
func_predict_player("A.Ekeler", "Chargers", "N.Chubb", "Browns", 15, 2021)
```


```{r}
func_rank_players_predicted <- function(player, teams, weeks, seasons){
  byWeek <- filter(fantasy_model, week == weeks, season == seasons)
  byWeek$rank <- min_rank(desc(byWeek$predictedFantasyPoints))
  result <- filter(byWeek, player_name == player, team == teams)
  return(sum(result$rank))
}
```

```{r}
func_rank_players <- function(player, teams, weeks, seasons){
  byWeek <- filter(fantasy_model, week == weeks, season == seasons)
  byWeek$rank <- min_rank(desc(byWeek$fantasy_points))
  result <- filter(byWeek, player_name == player, team == teams)
  return(sum(result$rank))
}
```

```{r}
func_rank_players("J.Conner", "Cardinals", 9, 2021)
```


```{r}
fantasy_model_train <- mutate(fantasy_model_train, 
                  predictedRank = mapply(func_rank_players_predicted, player_name, team, week, season),
                  rank = mapply(func_rank_players, player_name, team, week, season))
fantasy_model_test <- mutate(fantasy_model_test, 
                  predictedRank = mapply(func_rank_players_predicted, player_name, team, week, season),
                  rank = mapply(func_rank_players, player_name, team, week, season))
fantasy_model_test
```

```{r}
mean((fantasy_model_test$predictedRank - fantasy_model_test$rank)^2)
mean((fantasy_model_train$predictedRank - fantasy_model_train$rank)^2)
```

 
